\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\section{Background and Context}

\subsection{Attention Deficit Hyperactivity Disorder}
Attention Deficit Hyperactivity Disorder (ADHD) is a common and debilitating neurodevelopmental disorder thought to affect 3-5\% of the UK population. Symptoms can broadly be abstracted to either inattentiveness or hyperactivity and impulsivity, affecting individuals across both professional and personal life. Despite a up to 78% therapeutic response rate to ADHD medication, only ~8% of those with ADHD in the UK have been identified to receive a prescription. 
NICE guidelines state that individuals with ADHD should be provided  transitional, assessment and diagnostic services, as well as titration, monitoring and review of medication and psychological treatments. A lack of access to appropriate healthcare entails higher risks of substance misuse, criminality, and road traffic accidents among others. The current state of adult ADHD services in the UK, however, is burdened by unprecedented wait times of up to 4 years for assessment alone.  Access to medical intervention is further hindered by  fragmentation of service provision and national shortages of medication supply. The majority of patients is furthermore left dissatisfied with information on medication and alternative treatment provided by clinicians.
Therefore, now more than ever, those with ADHD as well as those questioning whether they have ADHD would benefit from a companion tool to help them gain control over their life and realistically face the impact caused by ADHD. These concepts are borrowed from the ‘Expert Patients Programme’ more often associated with chronic conditions such as diabetes and chronic fatigue. As ADHD however predisposes oneself to distractibility and a lack of adherence to routine among other issues, existing solutions may prove unsuitable, creating the niche I aim to explore. 

\subsubsection{Presentation}
\subsubsection{Diagnosis}
\subsubsection{Management}
\subsubsection{Digital Accessability Needs}
\subsection{Mobile Applications for Health Care Management}
\subsubsection{Monitoring Health Conditions}
\subsubsection{Managing Medication Schedules}
\subsection{\enquote{Nothing about me without me}}
\clearpage
\end{document}