\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\section{Work Carried Out}
\subsection{Application Prototype}
\subsubsection{Participatory Design}
Participants were included in the iterative design stage of the project. This was done to ensure that the application was designed with the needs of the target audience in mind.\\
Participants were required to meet the following criteria:
\beginitemize
    \item Be diagnosed with Dyslexia
    \item Be aged 18 or over
    \item Be able to communicate in English
\enditemize
Prior to commencing any Design or Developmemtal work an application for Ethical Approval by the Research Governance Team was submitted. Within the scope of the application a Participant Information Sheet (PIS), Promotional Flyer and Consent Form were drafted. \\
The PIS contains information on the background and aims of the project as well as consent, risks and benefits of participation as well as data protection and confidentiality. The Promotional Flyer condenses this information into an easily comprehensible format and features use of the OpenDyslexic Typeface for increased accesibility. The consent form similarly contains a distilled version of the PIS as well as statememnts regarding participartion eligibilty and consent to be confirmed by prospecive participants. \\
Participants were recruited from student led online groups centered around Disability and Neurodivergence. Upon reacting to promotional material they were first sent the consent form and subsequently an invitation to participate, given they met the participation criteria. \\
During an online interview they were asked to explore a prototype for \textit{Auxilium} and act out use case scenarios via the 'Think Aloud' Method. This allowed for real-time feedback on individual aspects of the user interface and feature set. Additionally they were asked to fill out a questionnaire to rate the usability of the system. This feedback was then used to inform the final iteration of the design.
\subsection{Development}
\subsubsection{Technology Stack}
\clearpage
\end{document}